## Functions for Data Transformations 

Function 1
This function takes as input the argument data.
It checks whether the dataset has a temperature variable and if so returns a new
column with the temperature converted from fahrenheit to celsius.

```{r}
convert_temp_to_celsius <- function(data) {
  
  # Check if the Temp column exists in the data
  if ("Temp" %in% names(data)) {
    # Convert Temp from Fahrenheit to Celsius
    data$Temp_C <- (data$Temp - 32) * (5 / 9)
    return(data)
  } else {
    stop("The data does not have a 'Temp' column.")
  }
}

# Running the function on R's airquality data
airquality_celsius <- convert_temp_to_celsius(airquality)
head(airquality_celsius)
```

Function 2
This function takes as input the argument data_new
It adds a new column, `Hot_Day`, to the provided dataset, which flags "hot" days. 
A day is considered "hot" (coded 1) if the temperature (`Temp` column) is above 70°F, 
or not (coded 0).

```{r}
add_hot_day_column <- function(data_new) {
  # Set the temperature threshold
  temp_threshold <- 70
  
  # Check if the Temp column exists in the data
  if ("Temp" %in% names(data_new)) {
    # Create a new column Hot_Day, set to 1 if Temp is above the threshold, otherwise 0
    data_new$Hot_Day <- ifelse(data_new$Temp > temp_threshold, 1, 0)
    return(data_new)
  } else {
    stop("The data does not have a 'Temp' column.")
  }
}

airquality_hotdays <- add_hot_day_column(airquality)
head(airquality_hotdays)
```



